---
title: Summary of results from CRU mentoring poll 
author:
  - Mark Scheuerell:
      email: scheuerl@uw.edu; mscheuerell@usgs.gov
      institute: wacfwru
      correspondence: true
institute:
  - wacfwru: U.S. Geological Survey Washington Cooperative Fish and Wildlife Research Unit, School of Aquatic and Fishery Sciences, University of Washington, Seattle, WA
output:
  pdf_document:
    highlight: haddock
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
documentclass: article
geometry: margin=1in
linestretch: 1.1
fontsize: 11pt
urlcolor: blue
header-includes:
  - \usepackage{lineno}
  - \linenumbers
bibliography: "references.bib"
csl: "frontiers-in-ecology-and-the-environment.csl"
---

```{r set_options, echo = FALSE, message = FALSE}
options(width = 100)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r citation_inits, echo = FALSE, message = FALSE}
## load package
# library("knitcitations")
## clean out any existing .bib files
# cleanbib()
## set pandoc for formatting
# options("citation_format" = "pandoc")
```


\vspace{0.2in}

This is version `r format(Sys.time(), '%y.%m.%d')`.


# Background

At the request of the CRU management team, the CRU DEI committee\footnote{DEI committee members are Graziella DiRenzo (MA), Angela Fuller (NY), J. Barry Grand (HQ); Mark Henderson (CA), Amanda Rosenberger (TN), Reynaldo Patino (TX), Mark Scheuerell (WA), Abby Powell (Chair; FL), Wendy Turner (WI).} developed an online survey to gather information about the mentoring needs and services of unit scientists and supervisors. The committee emailed a [link to the survey](https://forms.gle/nFUXpAcgTFv6xoQC8) via Shana Coulby in mid-October and asked people to respond within 3 weeks. Ultimately, we received responses from 60 individuals, which are summarized in this report.

# Survey topics

The survey included 6 general topics:

1) Administration

2) Career building

3) Conducting research

4) Coordination with partners

5) Lab management

6) Service

Within each topic, respondents were asked which format of mentoring they would prefer:

* One-on-one discussion

* Small group discussion

* Depends on the topic


## Administration



## Career building

## Conducting research

## Coordination with partners

## Lab management

## Service

