---
title: Summary of results from CRU mentoring poll 
author:
  - Mark Scheuerell:
      email: scheuerl@uw.edu; mscheuerell@usgs.gov
      institute: wacfwru
      correspondence: true
institute:
  - wacfwru: U.S. Geological Survey Washington Cooperative Fish and Wildlife Research Unit, School of Aquatic and Fishery Sciences, University of Washington, Seattle, WA
output:
  pdf_document:
    highlight: haddock
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
documentclass: article
geometry: margin=1in
linestretch: 1.1
fontsize: 11pt
urlcolor: blue
header-includes:
  - \usepackage{lineno}
  - \linenumbers
bibliography: "references.bib"
csl: "frontiers-in-ecology-and-the-environment.csl"
---

```{r set_options, echo = FALSE, message = FALSE}
options(width = 100)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r load_pkgs}
library(dplyr)
```

```{r citation_inits, echo = FALSE, message = FALSE}
## load package
# library("knitcitations")
## clean out any existing .bib files
# cleanbib()
## set pandoc for formatting
# options("citation_format" = "pandoc")
```


\vspace{0.2in}

This is version `r format(Sys.time(), '%y.%m.%d')`.


# Background

At the request of the CRU management team, the CRU DEI committee\footnote{DEI committee members are Graziella DiRenzo (MA), Angela Fuller (NY), J. Barry Grand (HQ); Mark Henderson (CA), Amanda Rosenberger (TN), Reynaldo Patino (TX), Mark Scheuerell (WA), Abby Powell (Chair; FL), Wendy Turner (WI).} developed an online survey to gather information about the mentoring needs and services of unit scientists and supervisors. The committee emailed a [link to the survey](https://forms.gle/nFUXpAcgTFv6xoQC8) via Shana Coulby in mid-October and asked people to respond within 3 weeks. Ultimately, we received responses from 60 individuals, which are summarized in this report.

# Survey topics

The survey included 6 general topics:

1) Administration

2) Career building

3) Conducting research

4) Coordination with partners

5) Lab management

6) Service

Within each topic, respondents were asked which format of mentoring they would prefer. Their options were a one-on-one discussion, a small group discussion, or that it would depend on the specific topic.

```{r read_data, echo = FALSE, message = FALSE}
data_raw <- readr::read_csv(here::here("data", "raw", "cru_peer_mentoring_survey.csv"))
```

## Administration

```{r extract_admin_data, echo = FALSE}
## extract admin data
data_admin <- data_raw %>%
  select(starts_with("Administration"))
```

```{r admin_responses, echo = FALSE, fig.align = "center", fig.dim = c(6,7), fig.cap = "Number of responses by role (mentor or mentee) for each of the administrative categories."}
## admin responses
responses_admin <- data_admin %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_admin == "Mentee" | responses_admin == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_admin == "Mentor" | responses_admin == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentees, mentors)

## list of topics
topics <- responses_admin %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2")

## plot response summary info
par(mai = c(0.9, 2.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("dodgerblue", "indianred"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.1, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

### Other administration topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_admin <- data_admin %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Administration topics [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_admin) {
    cat("*", topics, "\n\n")
}
```

```{r admin_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the administration category."}
## mentoring format
format_admin <- data_admin %>%
  select(contains("format"))

## mentoring format == depends
format_smry <- format_admin %>%
  table()

format_depends <- format_smry %>%
  names() %>%
  grep(pattern = "Depends")

## mentoring format summary
format_admin_smry <- c(format_smry[-format_depends], sum(format_smry[format_depends]))
names(format_admin_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_admin_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

## Career building

```{r extract_career_data, echo = FALSE}
## extract career data
data_career <- data_raw %>%
  select(starts_with("Career"))
```

```{r career_responses, echo = FALSE, fig.align = "center", fig.dim = c(6,5), fig.cap = "Number of responses by role (mentor or mentee) for each of the career categories."}
## admin responses
responses_career <- data_career %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_career == "Mentee" | responses_career == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_career == "Mentor" | responses_career == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentees, mentors)

## list of topics
topics <- responses_career %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2")

## plot response summary info
par(mai = c(0.9, 2.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("dodgerblue", "indianred"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.2, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

### Other career topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r career_other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_career <- data_career %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Career Building [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_career) {
    cat("*", topics, "\n\n")
}
```

```{r career_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the career category."}
## mentoring format
format_career <- data_career %>%
  select(contains("format"))

## mentoring format == depends
format_smry <- format_career %>%
  table()

format_depends <- format_smry %>%
  names() %>%
  grep(pattern = "Depends")

## mentoring format summary
format_career_smry <- c(format_smry[-format_depends], sum(format_smry[format_depends]))
names(format_career_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_career_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

## Conducting research

```{r extract_research_data, echo = FALSE}
## extract research data
data_research <- data_raw %>%
  select(starts_with("Conducting"))
```

```{r research_responses, echo = FALSE, fig.align = "center", fig.dim = c(6,4), fig.cap = "Number of responses by role (mentor or mentee) for each of the research categories."}
## research responses
responses_research <- data_research %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_research == "Mentee" | responses_research == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_research == "Mentor" | responses_research == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentees, mentors)

## list of topics
topics <- responses_research %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2")

## plot response summary info
par(mai = c(0.9, 2.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("dodgerblue", "indianred"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.3, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

### Other research topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r research_other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_research <- data_research %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Conducting Research [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_career) {
    cat("*", topics, "\n\n")
}
```

```{r research_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the research category."}
## mentoring format
format_research <- data_research %>%
  select(contains("format"))

## mentoring format == depends
format_smry <- format_research %>%
  table()

format_depends <- format_smry %>%
  names() %>%
  grep(pattern = "Depends")

## mentoring format summary
format_research_smry <- c(format_smry[-format_depends], sum(format_smry[format_depends]))
names(format_research_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_research_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

## Coordination with partners

## Lab management

## Service

