---
title: Summary of results from CRU mentoring poll 
author:
  - Mark Scheuerell:
      email: scheuerl@uw.edu; mscheuerell@usgs.gov
      institute: wacfwru
      correspondence: true
institute:
  - wacfwru: U.S. Geological Survey Washington Cooperative Fish and Wildlife Research Unit, School of Aquatic and Fishery Sciences, University of Washington, Seattle, WA
output:
  pdf_document:
    highlight: haddock
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
documentclass: article
geometry: margin=1in
linestretch: 1.1
fontsize: 11pt
urlcolor: blue
header-includes:
  - \usepackage{lineno}
  - \linenumbers
bibliography: "references.bib"
csl: "frontiers-in-ecology-and-the-environment.csl"
---

```{r set_options, echo = FALSE, message = FALSE}
options(width = 100)
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

```{r load_pkgs, echo = FALSE, message = FALSE}
library(dplyr)
```

```{r citation_inits, echo = FALSE, message = FALSE}
## load package
# library("knitcitations")
## clean out any existing .bib files
# cleanbib()
## set pandoc for formatting
# options("citation_format" = "pandoc")
```


\vspace{0.2in}

This is version `r format(Sys.time(), '%y.%m.%d')`.


# Background

At the request of the CRU management team, the CRU DEI committee\footnote{DEI committee members are Graziella DiRenzo (MA), Angela Fuller (NY), J. Barry Grand (HQ); Mark Henderson (CA), Amanda Rosenberger (TN), Reynaldo Patino (TX), Abby Powell (Chair; FL), Mark Scheuerell (WA), Wendy Turner (WI).} developed an online survey to gather information about the mentoring needs and services of unit scientists and supervisors. The committee emailed a [link to the survey](https://forms.gle/nFUXpAcgTFv6xoQC8) via Shana Coulby in mid-October and asked people to respond within 3 weeks. Ultimately, we received responses from 60 individuals, which are summarized in this report.

## Survey topics

The survey included 6 general topics:

1) Administration

2) Career building

3) Conducting research

4) Coordination with partners

5) Lab management

6) Service

Within each topic, respondents were asked which format of mentoring they would prefer. Their options were a one-on-one discussion, a small group discussion, or that it would depend on the specific topic.

```{r read_data, echo = FALSE, message = FALSE}
data_raw <- readr::read_csv(here::here("data", "raw", "cru_peer_mentoring_survey.csv"))
```
# Participant roles

Poll respondents were asked what primary role they felt they would play in a mentoring program. The responses were quite evenly mixed between "mentee", "mentor", and "both" (Figure 1).

\vspace{0.25in}

```{r roles, echo = FALSE, message = FALSE, fig.align = "center", fig.dim = c(4,2), fig.cap = "Number of respondents who would consider their primary role as mentee, mentor, or both."}

## participant roles
roles_smry <- data_raw %>%
  select(starts_with("In general")) %>%
  table()

## plot roles
par(mai = c(0.9, 0.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(roles_smry,
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

# Mentoring format

Poll respondents largely felt that the format or environment within which they would prefer to receive (or give) mentoring advice would depend on the specific topic. In general, though, relatively few people thought one-on-one meetings would be preferable relative to small group discussions (see figures on following pages).


\clearpage

# Administration

Among the many administrative tasks where unit staff could use some mentoring advice, "Use of Reston resources to enhance [a] program" and "Dealing with government sites & systems" received the most potential interest (Figure 2). The categories "Use of Reston resources to enhance program" and "Compliance with the Hatch Act" had the greatest disparity between the number of possible mentees and potential mentors.

\vspace{0.25in}

```{r extract_admin_data, echo = FALSE}
## extract admin data
data_admin <- data_raw %>%
  select(starts_with("Administration"))
```

```{r admin_responses, echo = FALSE, fig.align = "center", fig.dim = c(6,7), fig.cap = "Number of responses by role (mentee or mentor) for each of the administrative categories."}
## admin responses
responses_admin <- data_admin %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_admin == "Mentee" | responses_admin == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_admin == "Mentor" | responses_admin == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentors, mentees)

## list of topics
topics <- responses_admin %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2")

## plot response summary info
par(mai = c(0.9, 2.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("indianred", "dodgerblue"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.1, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

## Other administration topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_admin <- data_admin %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Administration topics [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_admin) {
    cat("*", topics, "\n\n")
}
```

## Mentoring format

\vspace{0.25in}

```{r admin_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the administration category."}
## mentoring format
format_admin <- data_admin %>%
  select(contains("format"))

## mentoring format != depends
format_smry <- format_admin %>%
  table()
format_other <- format_smry %>%
  names()
other_idx <- format_other == "One-on-one discussions" | format_other == "Small group discussions"

## mentoring format summary
format_admin_smry <- c(format_smry[other_idx], sum(format_smry[-other_idx]))
names(format_admin_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_admin_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

\clearpage

# Career building

Among the topics associated with career building, "Strategies for navigating the RGE process" was the most popular, but there is a clear need for those topics associated with personal well-being and achieving a proper work-life balance (Figure 4). In general, there was much better alignment between the number of possible mentees and potential mentors for this category.

\vspace{0.25in}

```{r extract_career_data, echo = FALSE}
## extract career data
data_career <- data_raw %>%
  select(starts_with("Career"))
```

```{r career_responses, echo = FALSE, fig.align = "center", fig.dim = c(6,5), fig.cap = "Number of responses by role (mentee or mentor) for each of the career categories."}
## admin responses
responses_career <- data_career %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_career == "Mentee" | responses_career == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_career == "Mentor" | responses_career == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentors, mentees)

## list of topics
topics <- responses_career %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2")

## plot response summary info
par(mai = c(0.9, 2.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("indianred", "dodgerblue"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.2, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

## Other career topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r career_other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_career <- data_career %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Career Building [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_career) {
    cat("*", topics, "\n\n")
}
```

## Mentoring format

\vspace{0.25in}

```{r career_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the career category."}
## mentoring format
format_career <- data_career %>%
  select(contains("format"))

## mentoring format != depends
format_smry <- format_career %>%
  table()
format_other <- format_smry %>%
  names()
other_idx <- format_other == "One-on-one discussions" | format_other == "Small group discussions"

## mentoring format summary
format_career_smry <- c(format_smry[other_idx], sum(format_smry[-other_idx]))
names(format_career_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_career_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

\clearpage

# Conducting research

Among the topics associated with conducting research, unit staff are clearly interested in more information about "Data archiving and ScienceBase", and there were very few people who felt they could serve as a mentor for this topic (Figure 6). Interestingly, there were more potential mentors than possible mentees for "Developing a research program".

\vspace{0.25in}

```{r extract_research_data, echo = FALSE}
## extract research data
data_research <- data_raw %>%
  select(starts_with("Conducting"))
```

```{r research_responses, echo = FALSE, fig.align = "center", fig.dim = c(6,4), fig.cap = "Number of responses by role (mentee or mentor) for each of the research categories."}
## research responses
responses_research <- data_research %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_research == "Mentee" | responses_research == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_research == "Mentor" | responses_research == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentors, mentees)

## list of topics
topics <- responses_research %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2")

## plot response summary info
par(mai = c(0.9, 2.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("indianred", "dodgerblue"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.3, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

## Other research topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r research_other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_research <- data_research %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Conducting Research [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_research) {
    cat("*", topics, "\n\n")
}
```

## Mentoring format

\vspace{0.25in}

```{r research_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the research category."}
## mentoring format
format_research <- data_research %>%
  select(contains("format"))

## mentoring format != depends
format_smry <- format_research %>%
  table()
format_other <- format_smry %>%
  names()
other_idx <- format_other == "One-on-one discussions" | format_other == "Small group discussions"

## mentoring format summary
format_research_smry <- c(format_smry[other_idx], sum(format_smry[-other_idx]))
names(format_research_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_research_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

\clearpage

# Coordination with partners

Perhaps not surprisingly, all of the topics within the category of coordination with partners received broad interest (Figure 8). Here, too, there were more potential mentors than possible mentees for "Working with cooperators" (and marginally so for "Funding").

\vspace{0.25in}

```{r extract_partners_data, echo = FALSE}
## extract partners data
data_partners <- data_raw %>%
  select(starts_with("Coordination"))
```

```{r partners_responses, echo = FALSE, fig.align = "center", fig.dim = c(6,4.5), fig.cap = "Number of responses by role (mentee or mentor) for each of the partners categories."}
## partners responses
responses_partners <- data_partners %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_partners == "Mentee" | responses_partners == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_partners == "Mentor" | responses_partners == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentors, mentees)

## list of topics
topics <- responses_partners %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2")

## plot response summary info
par(mai = c(0.9, 2.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("indianred", "dodgerblue"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.3, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

## Other partners topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r partners_other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_partners <- data_partners %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Coordination with partners [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_partners) {
    cat("*", topics, "\n\n")
}
```

## Mentoring format

\vspace{0.25in}

```{r partners_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the partners category."}
## mentoring format
format_partners <- data_partners %>%
  select(contains("format"))

## mentoring format != depends
format_smry <- format_partners %>%
  table()
format_other <- format_smry %>%
  names()
other_idx <- format_other == "One-on-one discussions" | format_other == "Small group discussions"

## mentoring format summary
format_partners_smry <- c(format_smry[other_idx], sum(format_smry[-other_idx]))
names(format_partners_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_partners_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

\clearpage

# Lab management

The topics within the lab management category all received considerable interest (Figure 10). Many of these topics focus on elements of diversity, equity, inclusion, and justice, which is perhaps not too surprising. Of note, the topic of "DEIJ outreach & broader impacts" had very few potential mentors and wide interest among respondents. The topic of "Teaching/developing a course" had more potential mentors than possible mentees, as did "Mentoring students".

\vspace{0.25in}

```{r extract_lab_data, echo = FALSE}
## extract lab data
data_lab <- data_raw %>%
  select(starts_with("Lab"))
```

```{r lab_responses, echo = FALSE, fig.align = "center", fig.dim = c(7, 5), fig.cap = "Number of responses by role (mentee or mentor) for each of the lab categories."}
## lab responses
responses_lab <- data_lab %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_lab == "Mentee" | responses_lab == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_lab == "Mentor" | responses_lab == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentors, mentees)

## list of topics
topics <- responses_lab %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2") %>%
  sub(pattern = "(local high schools, mentoring programs, etc.) ",
      replacement = "", fixed = TRUE)

## plot response summary info
par(mai = c(0.9, 3.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("indianred", "dodgerblue"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.2, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

## Other lab topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r lab_other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_lab <- data_lab %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Lab Management [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_lab) {
    cat("*", topics, "\n\n")
}
```

\clearpage

## Mentoring format

\vspace{0.25in}

```{r lab_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the lab management category."}
## mentoring format
format_lab <- data_lab %>%
  select(contains("format"))

## mentoring format != depends
format_smry <- format_lab %>%
  table()
format_other <- format_smry %>%
  names()
other_idx <- format_other == "One-on-one discussions" | format_other == "Small group discussions"

## mentoring format summary
format_lab_smry <- c(format_smry[other_idx], sum(format_smry[-other_idx]))
names(format_lab_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_lab_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

\clearpage

# Service

All of the topics within the service category were generally quite popular, but especially "Communication & social media", which also had the greatest discrepancy between possible mentees and mentors (Figure 12). Notably, the categories of "Providing constructive reviews" and "Involvement in professional organizations and meetings" had more potential mentors than interested mentees.

\vspace{0.25in}

```{r extract_service_data, echo = FALSE}
## extract service data
data_service <- data_raw %>%
  select(starts_with("Service"))
```

```{r service_responses, echo = FALSE, fig.align = "center", fig.dim = c(7, 5), fig.cap = "Number of responses by role (mentee or mentor) for each of the service categories."}
## service responses
responses_service <- data_service %>%
  select(!contains("format")) %>%
  select(!contains("other topics"))

## number of mentees
mentees <- (responses_service == "Mentee" | responses_service == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## number of mentors
mentors <- (responses_service == "Mentor" | responses_service == "Mentor;Mentee") %>%
  apply(2, sum, na.rm = TRUE)

## matrix of data for plotting
data_plot <- rbind(mentors, mentees)

## list of topics
topics <- responses_service %>%
  colnames() %>%
  sub(pattern = "(^.*\\[)(.*)(\\])", replacement = "\\2") %>%
  sub(pattern = "Service (editor",
      replacement = "Editor", fixed = TRUE) %>%
  sub(pattern = "etc)",
      replacement = "etc", fixed = TRUE)

## plot response summary info
par(mai = c(0.9, 3.9, 1, 0.1),
    omi = rep(0.1, 4))
barplot(data_plot, beside = TRUE,
        col = c("indianred", "dodgerblue"), border = NA,
        names.arg = topics,
        legend.text = TRUE,
        args.legend = list(x = "top", inset = -0.2, bty = "n", border = NA,
                           xpd = TRUE, cex = 0.8),
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")
```

## Other service topics

Poll respondents were offered an opportunity to add other topics for which they would like some mentoring advice. Here is a list of those responses. 

```{r service_other_topics, echo = FALSE, results = 'asis'}
## other topics
other_topics_service <- data_service %>%
  select(contains("other topics")) %>%
  unique() %>%
  filter(`Service [other topics]` != is.na(.)) %>%
  pull()

for (topics in other_topics_service) {
    cat("*", topics, "\n\n")
}
```

\clearpage

## Mentoring format

\vspace{0.25in}

```{r service_formats, echo = FALSE, fig.align = "center", fig.dim = c(6,2), fig.cap = "Number of responses for each of the proposed mentoring formats for the service category."}
## mentoring format
format_service <- data_service %>%
  select(contains("format"))

## mentoring format != depends
format_smry <- format_service %>%
  table()
format_other <- format_smry %>%
  names()
other_idx <- format_other == "One-on-one discussions" | format_other == "Small group discussions"

## mentoring format summary
format_service_smry <- c(format_smry[other_idx], sum(format_smry[-other_idx]))
names(format_service_smry)[3] <- "Depends on the topic"

## plot response summary info
par(mai = c(0.9, 2.9, 0.1, 0.1),
    omi = rep(0.1, 4))
barplot(rev(format_service_smry),
        border = NA,
        horiz = TRUE, las = 1, cex.names = 0.8,
        xlab = "Number of responses")

```

